---
title: "Bridge Data Science Math HW 3"
author: "mehtablocker"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Exercises 1 - 5

#### Exercise 1
`r round( pnorm(979, mean = 1300, sd = sqrt(40000), lower.tail = F), 4)`

#### Exercise 2
`r round( pnorm(8340, mean = 11000, sd = sqrt(1960000), lower.tail = F), 4)`

#### Exercise 3
`r round( pnorm(85, mean = 80, sd = 3, lower.tail = T) - pnorm(83, mean = 80, sd = 3, lower.tail = T), 4)`

#### Exercise 4
`r round( qnorm(.14, mean = 456, sd = 123, lower.tail = F), 0)`

#### Exercise 5
`r round( qnorm(c(0.07, 1-0.07), mean = 6.13, sd = 0.06, lower.tail = T), 2)`

## Exercises 6 - 10

#### Exercise 6
`r round( qnorm(c(0.20, 1-0.45), mean = 78.8, sd = 9.8, lower.tail = T), 0)`

#### Exercise 7
`r round( qnorm(1-0.45, mean = 21.2, sd = 5.4, lower.tail = T), 1)`

#### Exercise 8
`r round( pnorm(11, mean = 151*0.09, sd = sqrt(151*0.09*(1-0.09)), lower.tail = T), 4)`

#### Exercise 9
`r round( pnorm(48.83, mean = 48, sd = 7/sqrt(147), lower.tail = F), 4)`

#### Exercise 10
`r round( pnorm(93.54, mean = 91, sd = 10/sqrt(68), lower.tail = F), 4)`

## Exercises 11 - 15

#### Exercise 11
`r round( diff(pnorm(c(540*0.07*0.97, 540*0.07*1.03), mean = 540*0.07, sd = sqrt(0.07*(1-0.07)/540), lower.tail = T)), 4)`

#### Exercise 12
`r round( pnorm(602*0.23*0.96, mean = 602*0.23, sd = sqrt(0.23*(1-0.23)/602), lower.tail = T) + pnorm(602*0.23*1.04, mean = 602*0.23, sd = sqrt(0.23*(1-0.23)/602), lower.tail = F), 4)`

#### Exercise 13
`r round( qnorm(c(0.1, 0.9), mean = 3.9, sd = 0.8/sqrt(208), lower.tail = T), 1)`

#### Exercise 14
`r round( qnorm(c(0.01, 0.99), mean = 16.6, sd = 11/sqrt(7472), lower.tail = T), 1)`

#### Exercise 15
Step 1: Top right

Step 2: 
`r round( qt(0.05, df = 26, lower.tail = F), 1)`

## Exercises 16 - 18

#### Exercise 16
```{r ex_16}
values <- c(383.6, 347.1, 371.9, 347.6, 325.8, 337)
n <- length(values)
df <- n - 1
ci <- 0.90
alpha <- (1-ci)/2

## Step 1
x_bar <- round(mean(values), 2)
x_bar

## Step 2
s <- round(sd(values), 2)
s

## Step 3
t_score <- round(qt(alpha, df=df, lower.tail = F), 3)
t_score

## Step 4
round(x_bar - t_score * (s / sqrt(n)), 2)
round(x_bar + t_score * (s / sqrt(n)), 2)

```

#### Exercise 17
```{r ex_17}
x_bar <- 46.4
s <- 2.45
n <- 16
df <- n - 1
ci <- 0.80
alpha <- (1-ci)/2

## Step 1
t_score <- round(qt(alpha, df=df, lower.tail = F), 3)
t_score

## Step 2
round(x_bar - t_score * (s / sqrt(n)), 2)
round(x_bar + t_score * (s / sqrt(n)), 2)

```

#### Exercise 18
Assuming the previous study was exhaustive enough to be comfortable using 1.9 as a population sd:  
`r ceiling((qnorm(0.995)*1.9/0.13)^2)`

## Exercises 19 - 21

#### Exercise 19
`r ceiling((qnorm(0.975)*sqrt(3.61)/0.19)^2)`

#### Exercise 20
```{r ex_20}
## Step 1
x <- 1734
n <- 2089
p <- round(1-x/n, 3)
p

## Step 2
round(p - qnorm(0.99)*sqrt(p*(1-p)/n), 3)
round(p + qnorm(0.99)*sqrt(p*(1-p)/n), 3)

```

#### Exercise 21
```{r ex_21}
## Step 1
x <- 156
n <- 474
p <- round(x/n, 3)
p

## Step 2
round(p - qnorm(0.975)*sqrt(p*(1-p)/n), 3)
round(p + qnorm(0.975)*sqrt(p*(1-p)/n), 3)

```
