---
title: "Data Science Math HW 1"
author: "mehtablocker"
date: "December 26, 2018"
output:
  html_document:
    toc: true
    toc_float: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

  
##Derivatives

```{r include=F}
library(Deriv)
solution1 <- Deriv(function(x) 1-exp(-lambda * x))
solution2 <- Deriv(function(x) (x-a) / (b-a))
solution3 <- Deriv(function(x) (x-a)^2 / ((b-a) * (c-a)))
solution4 <- Deriv(function(x) 1 - (b-x)^2 / ((b-a) * (c-a)))
```

####Exercise 1
$$ `r deparse(solution1)[2]` $$

####Exercise 2
$$ `r deparse(solution2)[2]` $$

####Exercise 3
$$ `r deparse(solution3)[2]` $$

####Exercise 4
$$ `r deparse(solution4)[2]` $$

  
## Integrals

```{r include=F}
myfunc5 <- function(x) 3 * x^3
solution5 <- integrate(myfunc5, 0, 10)
library(mosaicCalc)
```

####Exercise 5
$$ `r as.character(solution5)[1]` $$

####Exercise 6
integration by parts using derivative from above  
u = x, dv = 
```{r echo=T}
Deriv(function (x) 1 - exp(-1 * lambda * x))
```

du = dx, v = 1 - exp(-1 * lambda * x)  
  
integral of vdx:
```{r echo=T}
antiD(1-exp(-1 * lambda * x) ~ x)
```

subtract that from vu to get final answer:

$$ e^{-\lambda x} * (\frac{1}{-\lambda} - x) $$

####Exercise 7
```{r echo = T}
antiD(1/(b-a) ~ x)
```

$$ (0.5) / (b-a) $$

####Exercise 8
integration by parts by multiplying the given equation by $\frac{1}{(B^\alpha)^2}$  
u = $x * \frac{1}{(B^\alpha)^2}$, dv = gamma_pdf

```{r echo=T}
Deriv(function (x) x * 1/(B^a)^2)
```

du = $\frac{1}{B^{2\alpha}}$ dx, v = gamma_cdf [because cdf is the integral of pdf]  
  
vu - $\int$vdu =  
  
gamma_cdf $* x * \frac{1}{(B^\alpha)^2}$ - $\int \frac{1}{B^{2\alpha}} *$ gamma_cdf dx

  
## Linear Algebra

```{r echo=F}
X <- rbind(c(1, 2, 3),
           c(3, 3, 1),
           c(4, 6, 8))
m2l <- function(matr) {

    printmrow <- function(x) {

        ret <- paste(paste(x,collapse = " & "),"\\\\")
        sprintf(ret)
    }

    out <- apply(matr,1,printmrow)
    out2 <- paste("\\begin{bmatrix}",paste(out,collapse=' '),"\\end{bmatrix}")
    return(out2)
}
```

####Exercise 9
$$ X = `r m2l(X)` $$
Augment with
$$ `r m2l(diag(1,3))` $$
and perform row reduction until left with:
$$ `r m2l(matrix(c(-4.5, -0.5, 1.75, 5, 1, -2, -1.5, -0.5, 0.75), nrow=3, byrow=T))` $$

####Exercise 10
```{r echo=T}
det(X)
```

####Exercise 11
We can find U easily through elimination.
This results in U=
$$ `r m2l(matrix(c(1, 2, 3, 0, -3, -8, 0, 0, round(1+1/3,2)), nrow=3, byrow=T))` $$
And since LU = X that means  
$$ (L)(U)(U^{-1})(L^{-1}) = (X)(X^{-1})$$
and therefore  
$$ (U^{-1})(L^{-1}) = (X^{-1})$$

So we can find L:
```{r echo=T}
U <- rbind(c(1, 2, 3),
           c(0, -3, -8),
           c(0, 0, 1+1/3))
L <- solve(solve(solve(U), solve(X)))
```
L = 
$$ `r m2l(round(L,2))` $$

####Exercise 12
```{r echo=T}
solution12 <- round(X %*% solve(X))
```
$$ `r m2l(solution12)` $$